\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
naamsverandering
paper updates

%------------------------------------------------
\section{Proof of Correctness}
NOG NIET AF!
\begin{definition}
A \emph{colored} graph $G(E,V)$ is a graph where each vertex $v \in V$ has a color label.
\end{definition}
\begin{definition}
Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs. A function $f: V_1 \to V_2$ is called a \emph{graph isomorphism} if (a) $f$ is a bijection, (b) for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and (c) $color(v)$ = $color (f(v)$. When such a function exist, $G_1$ and $G_2$ are called \emph{isomorphic graphs}. 
\end{definition}
\begin{theorem}
Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs where each vertex has the same color and let $H_1 = (V_1, E_1)$ and $H_2 = (V_2, E_2)$ be resp. the same graphs as $G_1$ and $G_2$ where each (false) twin is replaced by a colored vertex such that: \begin{enumerate}
\item Twins (False twins) have the same color $\iff$ Twins (False twins) have the same size (number of vertices).
\item A twin and a false twin can't have the same color.
\end{enumerate}
Graph $G_1$ and $G_2$ are isomorphic $\iff$ Graph $H_1$ and $H_2$ are isomorphic.
\begin{proof}
Todo
\end{proof}

>>>>

%------------------------------------------------
\section{Proof of Correctness}
NOG NIET AF!
\begin{definition}
A \emph{colored} graph $G(E,V)$ is a graph where each vertex $v \in V$ has a color label.
\end{definition}
\begin{definition}
Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs. A function $f: V_1 \to V_2$ is called a \emph{graph isomorphism} if \begin{compactenum}[\upshape(a)]
\item $f$ is a bijection, 
\item for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and 
\item $color(v)$ = $color (f(v)$. When such a function exist, $G_1$ and $G_2$ are called \emph{isomorphic graphs}. 
\end{compactenum}
\end{definition}
\begin{theorem}
Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs where each vertex has the same color and let $H_1 = (V_1, E_1)$ and $H_2 = (V_2, E_2)$ be resp. the same graphs as $G_1$ and $G_2$ where each (false) twin is replaced by a colored vertex such that: \begin{compactenum}[\upshape(a)]
\item Twins (False twins) have the same color $\iff$ Twins (False twins) have the same size (number of vertices).
\item A twin and a false twin can't have the same color.
\end{compactenum}
Graph $G_1$ and $G_2$ are isomorphic $\iff$ Graph $H_1$ and $H_2$ are isomorphic.
\end{theorem}
\begin{proof}
Todo
\end{proof}
